---
title: "Final_Report"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
library(rvest)
library(openintro)
library(ggmap)
library(patchwork)
library(modelr)
library(purrr)
library(flexdashboard)
library(viridis)
library(plotly)
library(stringr)
library(p8105.datasets)
library(kableExtra)
library(shiny)
```

## Team Members and UNIs:

Melanie Mayer; mm4963  
Jaisal Amin; ja3314  
Rebekah Yu; dry2115  
Courtney Johnson; cj2493  
  
## Motivation, Background, and Initial Questions:  

Motivation for this project was rooted in the group's collective interest in the impact of public health initiatives on health outcomes. While exploring for related datasets, we found city-level data on health practices and health outcomes from the CDC. Project objectives and analysis plans were mainly driven by the data and the information available from the data set. 

The initial question we explored was what are the associations between:
  (1) prevalence of lack of health insurance, 
  (2) regular health practices (i.e. pap smear, doctor visits, mammograms), and 
  (3) health outcomes (diabetes, kidney disease, smoking). 
  
To further support our analysis, we hypothesized that health expenditures could be a possible predictor of outcomes and practices, thus, an external data set of health expenditures by state was included. In addition, we were interested in regional trends of health for the data. To obtain regional categories, we found an external data set including four regions and states included in each region. 


## Data:  

Our data was taken from the 500 cities project. The data used for their analysis was obtained from the Centers of Disease Control, Division of Population Health, Epidemiology, and Surveillance Branch. The dataset provides model-based estimates for the prevalence of various diseases/practices in order to help local public health officials better serve their communities. We filtered out many variables and ultimately chose to only keep diseases associated with higher rates of fatality and/or those that placed a higher burden on our healthcare system. We also kept variables that could be clearly classified as "health practices" or behaviors whose primary purpose is to maintain or improve one's health. Because we were interested in the relationship between these variables and health insurance/expenditure, we kept the variable associated with prevalence of lack of insurance and imported data on healthcare expenditure by state from the Henry J. Kaiser Family Foundation. In order to conduct regional analysis, we imported a dataset that classified states based on region.  

Link to original data set from the CDC:
https://chronicdata.cdc.gov/500-Cities/500-Cities-City-level-Data-GIS-Friendly-Format-201/k56w-7tny/data

When attempting to extract the data using the API, some variables (such as city name and state) were dropped in the process. Our data was obtained and completed in 2016, so we found it appropriate to simply download the CSV to use for our analysis. Below is the link to the data set that was read in for our project:
https://drive.google.com/file/d/1ltT_y_W5kveipbEq6smnpsjmVADIwnee/view?usp=sharing

Data for health care expenditure was downloaded from the Henry J. Kaiser Family Foundation
Link to our health care expenditure data:
https://drive.google.com/file/d/1jlps3e265Q9eZoBXcgKTu5YrKwOOHTFc/view?usp=sharing

Data for state and region categories were found on Chris Halpert's github.
Link to region and state data:
https://drive.google.com/file/d/1jlps3e265Q9eZoBXcgKTu5YrKwOOHTFc/view?usp=sharing

### Instructions for reading in data:
Download the data sets from the google drive links given above. In the code below, replace the "read_csv" locations to the local locations where data is downloaded.

Code for reading in, merging, and cleaning data:
```{r}
cdc_df = read_csv("./data/500_Cities__City-level_Data__GIS_Friendly_Format___2016_release.csv")
#Select variables of interest
cdc_df = cdc_df %>%
  select(c(StateAbbr, PlaceName, Population2010, ACCESS2_AdjPrev, BPHIGH_AdjPrev, BPMED_AdjPrev, CANCER_AdjPrev, CHD_AdjPrev, CHECKUP_AdjPrev, CHOLSCREEN_AdjPrev, COLON_SCREEN_AdjPrev, COPD_AdjPrev,COREM_AdjPrev, COREW_AdjPrev, DENTAL_AdjPrev, DIABETES_AdjPrev, HIGHCHOL_AdjPrev, LPA_AdjPrev, MAMMOUSE_AdjPrev, OBESITY_AdjPrev, PAPTEST_AdjPrev, PHLTH_AdjPrev, STROKE_AdjPrev, Geolocation)) %>% 
  mutate(state = abbr2state(StateAbbr)) %>%
  select(state, everything())
#Importing the raw expenditure data set and cleaning
healthcare_exp_df = read_csv("./data/health_care_expenditure.csv", 
                             skip = 4, n_max = 51, col_names = F) %>%
  rename(state = "X1", health_exp = "X2") %>%
  mutate(health_exp = str_replace(health_exp, "\\$", ""),
         health_exp  = as.numeric(health_exp))
#Add state healthcare expenditure data to CDC data
cdc_df = left_join(cdc_df, healthcare_exp_df, by = "state")
cdc_df = cdc_df %>% mutate(state = abbr2state(StateAbbr))
#Merge data regions per state
regions_df = read_csv("https://raw.githubusercontent.com/cphalpert/census-regions/master/us%20census%20bureau%20regions%20and%20divisions.csv") %>%
  janitor::clean_names() %>%
  select(-state_code)
  
cdc_df = left_join(cdc_df, regions_df, by = "state")
```


Similar to downloading our initial data, variable obtaining issues progressed when attempting to scrape the data for our data dictionary. Therefore, we copied the data dictionary given on the website and pasted into an excel file. Below is the link to the excel data dictionary file:

https://drive.google.com/file/d/1Myn3kicEjmmeD2PGoOehSlA30UtFfaV9/view?usp=sharing

  
Code to create a data dictionary: 
```{r, data_dictionary}
data_dictionary = readxl::read_xlsx("./data/data_dictionary.xlsx") 
data_dictionary = data_dictionary %>%
  janitor::clean_names() %>%
  filter(column_name %in% c("StateAbbr", "PlaceName", "Population2010", "ACCESS2_AdjPrev", "BPHIGH_AdjPrev", "BPMED_AdjPrev", "CANCER_AdjPrev", "CHD_AdjPrev", "CHECKUP_AdjPrev", "CHOLSCREEN_AdjPrev", "COLON_SCREEN_AdjPrev", "COPD_AdjPrev", "COREM_AdjPrev", "COREW_AdjPrev", "DENTAL_AdjPrev", "DIABETES_AdjPrev", "HIGHCHOL_AdjPrev", "LPA_AdjPrev", "MAMMOUSE_AdjPrev", "OBESITY_AdjPrev", "PAPTEST_AdjPrev", "PHLTH_AdjPrev", "STROKE_AdjPrev", "Geolocation"))
health_exp_dictionary = tibble(column_name = c("state", "health_exp"),
                               description = c("full name of the state", "total healthcare expenditures per capita by state in 2014"),
                               type = c("Plain Text", "Number"))
data_dictionary = full_join(data_dictionary, health_exp_dictionary)
region_dict = tibble(column_name = c("region", "division"),
                     description = c("geographical region of the state", "more specific division within the region"),
                     type = c("Plain Text", "Plain Text")
)
data_dictionary = full_join(data_dictionary, region_dict)
```


## Exploratory Analysis:  
Shiny plots were created to explore the associations between health factors and health outcomes. We defined two health factors of interest: (1) prevalence of uninsured people by city and (2) health care expenditure by state. To give visualizations of the type of plots created, the code below illustrates the plots for the health outcome, cancer. However, in the Shiny document, users can toggle between 9 outcomes.

```{r}
# transform data to long form
outcome_transform = cdc_df %>% 
  mutate(city_state = str_c(PlaceName, StateAbbr, sep = ", ")) %>%
  gather(key = outcome, value = prevalence, BPHIGH_AdjPrev, CANCER_AdjPrev, CHD_AdjPrev, COPD_AdjPrev,    DIABETES_AdjPrev, HIGHCHOL_AdjPrev, OBESITY_AdjPrev, PHLTH_AdjPrev, STROKE_AdjPrev) %>% 
  mutate(outcome = str_replace(outcome, "_AdjPrev", ""), 
        outcome = recode(outcome, 'BPHIGH' = 'High Blood Pressure',
                                  'CANCER' = 'Cancer',
                                  'CHD' = 'Coronary Heart Disease',
                                  'COPD' = 'Chronic Obstructive Pulmonary Disease',
                                  'DIABETES' = 'Diabetes',
                                  'HIGHCHOL' = 'High Cholesterol',
                                  'OBESITY' = 'Obesity',
                                  'PHLTH' = 'Poor Physical Health',
                                  'STROKE' = 'Stroke')) %>%
  select(city_state, ACCESS2_AdjPrev, Population2010, Geolocation, health_exp, region, division, outcome, prevalence) 
# Plot of Prevalence of Cancer vs. Prevalence of Uninsured
outcome_transform %>%
  filter(outcome == "Cancer") %>%
  ggplot(aes(x = ACCESS2_AdjPrev, y = prevalence, color = region)) +
    geom_point(alpha = 0.5) +
    labs(
      x = "Prevalence of Uninsured in City",
      y = "Prevalence of Cancer")
#Plot of Prevalence of Cancer vs. Health Care Expenditures
outcome_transform %>%
  filter(outcome == "Cancer") %>%
  ggplot(aes(x = health_exp, y = prevalence, color = region)) +
    geom_point(alpha = 0.5) +
    labs(
      x = "Health Expenditure",
      y = "Prevalence of Health Outcome (millions)")
```

From the plots above, we see that as the percentage of uninsured people increase, the prevalence of cancer decreases. This trend could be explained by the fact that the more people who are uninsured, the less screening for cancer is done, and thus there is a smaller prevalence of diagnosed cancer recorded. There is not an obvious trend for health care expenditures and cancer prevalence. We use the Shiny app to look at the associations with different health outcomes.


## Additional Analysis:  

### Regression Analysis: 

To explore the relationship between commonly used health practices and health outcomes, we tried to fit some multiple linear regression models using backwards selection.  The models we created were attempting to predict the prevalence of cancer, high cholesterol and diabetes. For each model, we started with all of the health practice variables: core screenings for men, core screenings for women, dental visits, lack of physical activity, mammogram usage, routine checkups, 
cholesterol screenings, and colon screenings. All of these variables are also in terms of prevalence. Then, to show the results in a way that people who aren't statisticians could understand, I produced a table for each model that showed which variables were included in the final model and the direction of effect they had on the disease prevalence.  

```{r, cancer_model, include = FALSE}
cancer_full_mod = lm(CANCER_AdjPrev ~ COREM_AdjPrev + COREW_AdjPrev + DENTAL_AdjPrev + LPA_AdjPrev + MAMMOUSE_AdjPrev + PAPTEST_AdjPrev + CHECKUP_AdjPrev + CHOLSCREEN_AdjPrev + COLON_SCREEN_AdjPrev, data = cdc_df)
summary(cancer_full_mod)
cancer_minus_1 = update(cancer_full_mod, . ~ . -COREW_AdjPrev)
summary(cancer_minus_1)
cancer_minus_2 = update(cancer_minus_1, . ~ . -LPA_AdjPrev)
summary(cancer_minus_2)
cancer_minus_3 = update(cancer_minus_2, . ~ . -CHOLSCREEN_AdjPrev)
summary(cancer_minus_3)
cancer_minus_4 = update(cancer_minus_3, . ~ . -PAPTEST_AdjPrev)
summary(cancer_minus_4)
```

```{r, cancer_tbl}
health_practice = c("Core Practices for Men", "Dental Visits", "Mammogram Usage",
                    "Routine Checkups", "Colon Screening")
effect = c("Positive", "Negative", "Negative", "Negative", "Positive")
estimate = c(0.012, -0.033, -0.036, -0.0095, 0.107)
p_val = c(0.012, '1.06e-14', '2.31e-06', 0.0295, '< 2e-16')
cancer_tbl = tibble(
  "Health Practice" = health_practice,
  "Effect on Cancer Prevalence" = effect,
  "Coefficient Estimate" = estimate,
  "P-Value" = p_val
)
cancer_tbl %>%
  knitr::kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "center")
```

```{r, chol_model, include = FALSE}
chol_full_mod = lm(HIGHCHOL_AdjPrev ~ COREM_AdjPrev + COREW_AdjPrev + DENTAL_AdjPrev + LPA_AdjPrev + MAMMOUSE_AdjPrev + PAPTEST_AdjPrev + CHECKUP_AdjPrev + CHOLSCREEN_AdjPrev + COLON_SCREEN_AdjPrev, data = cdc_df)
summary(chol_full_mod)
chol_minus_1 = update(chol_full_mod, . ~ . -CHOLSCREEN_AdjPrev) 
summary(chol_minus_1)
chol_minus_2 = update(chol_minus_1, . ~ . -COREW_AdjPrev)
summary(chol_minus_2)
chol_minus_3 = update(chol_minus_2, . ~ . -COREM_AdjPrev)
summary(chol_minus_3)
chol_minus_4 = update(chol_minus_3, . ~ . -MAMMOUSE_AdjPrev)
summary(chol_minus_4)
chol_minus_5 = update(chol_minus_4, . ~ . -PAPTEST_AdjPrev)
summary(chol_minus_5)
```

```{r, chol_tbl}
health_practice = c("Dental Visits", "Lack of Physical Activity",
                    "Routine Checkups", "Colon Screening")
effect = c("Negative", "Positive", "Positive", "Positive")
estimate = c(-0.064, 0.171, 0.0401, 0.061)
p_val = c(0.004, '9.18e-07', 0.049, 0.037)
chol_tbl = tibble(
  "Health Practice" = health_practice,
  "Effect on High Cholesterol Prevalence" = effect,
  "Coefficient Estimate" = estimate,
  "P-Value" = p_val
)
chol_tbl %>%
  knitr::kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "center")
```

```{r, diab_model, include = FALSE}
diab_full_mod = lm(DIABETES_AdjPrev ~ COREM_AdjPrev + COREW_AdjPrev + DENTAL_AdjPrev + LPA_AdjPrev + MAMMOUSE_AdjPrev + PAPTEST_AdjPrev + CHECKUP_AdjPrev + CHOLSCREEN_AdjPrev + COLON_SCREEN_AdjPrev, data = cdc_df)
summary(diab_full_mod)
diab_minus_1 = update(diab_full_mod, . ~ . -COLON_SCREEN_AdjPrev)
summary(diab_minus_1)
diab_minus_2 = update(diab_minus_1, . ~ . -PAPTEST_AdjPrev)
summary(diab_minus_2)
diab_minus_3 = update(diab_minus_2, . ~ . -COREM_AdjPrev)
summary(diab_minus_3)
```

```{r, diab_tbl}
health_practice = c("Core Practices for Women", "Dental Visits", "Lack of Physical Activity", "Mammogram Usage", "Routine Checkups", "Cholesterol Screening")
effect = c("Negative", "Negative", "Positive", "Positive", "Positive", "Negative")
estimate = c(-0.063, -0.135, 0.193, 0.085, 0.076, -0.074)
p_val = c('6.19e-11', '< 2e-16', '< 2e-16', '1.44e-08', '1.33e-08', 0.0004)
diab_tbl = tibble(
  "Health Practice" = health_practice,
  "Effect on Diabetes Prevalence" = effect,
  "Coefficient Estimate" = estimate,
  "P-Value" = p_val
)
diab_tbl %>%
  knitr::kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "center")
```

We ran simple linear regressions to determine if there was an association between the prevalence of lack of insurance and the prevalence of health outcomes -- colon/cancer/cholestrol screenings, mammograms, etc. The purpose here was not to build a predictive model, only to test association and therefore any statistics related to model reliability were disregarded.

```{r, insurance_slrs}
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ CHECKUP_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ DENTAL_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ CHOLSCREEN_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ COLON_SCREEN_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ COREM_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ COREW_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ LPA_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ MAMMOUSE_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ PAPTEST_AdjPrev, data = .) %>%
  summary
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ PHLTH_AdjPrev, data = .) %>%
  summary
```

```{r, insurance_tbl}
health_practice = c("Health Checkup", "Cholestrol Screening", "Colon Screening", "Dental", "COREM", "COREW", "LPA", "Mammogram", "Pap Test", "Poor Physical Health")
linear = c("No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")
direction = c("NA", "Negative", "Negative", "Negative", "Negative", "Negative", "Positive", "Negative", "Negative", "Positive")
p_value = c(0.711, '<2e-16', '<2e-16', '<2e-16', '<2e-16', '<2e-16', '<2e-16', '<2e-16', '<2e-16', '<2e-16')
insurance_asso = tibble(
  "Health Practice" = health_practice,
  "Linear Association?" = linear,
  "Direction of Association" = direction,
  "p-value" = p_value
) 
insurance_asso %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = T, position = "center")
```

```{r, insurance_plots}
dental = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = DENTAL_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("Dental")
colon = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = COLON_SCREEN_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("Colon Screening")
lpa = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = LPA_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("No Physical Activity")
phlth = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = PHLTH_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("Poor Physical Health")
(dental | colon) / (lpa | phlth)
```

We also wanted to look at lack of health insurance prevalence and health expenditure by state and compare across regions. We created graphs to display differences and ran an ANOVA to test significance.

```{r, insurance_map, cache = TRUE}
usa = map_data("state") %>%
  rename(state = "region")
cdc_df_map = read_csv("./data/cdc_df.csv") %>%
  separate(Geolocation, into = c("long", "lat"), sep = ",") %>%
  mutate(long = str_replace(long, "\\(", ""),
         lat = str_replace(lat, "\\)", ""),
         long = as.numeric(long),
         lat = as.numeric(lat),
         state = factor(state),
         state = tolower(state)) %>%
  filter(!state %in% c("alaska", "hawaii")) %>%
  left_join(., usa, by = "state")
ggplot() + 
  geom_polygon(data = cdc_df_map, aes(x = long.y, y = lat.y, group = state, 
                                      fill = ACCESS2_AdjPrev), 
               color = "white") +
  scale_fill_gradient2(low = "dark blue", mid = "white", high = "red", space = "Lab",
                       midpoint = mean(cdc_df_map$ACCESS2_AdjPrev),
                       name = "% Lacking") +
  coord_fixed(1) +
  geom_point(data = cdc_df_map, aes(x = lat.x, y = long.x), 
             color = "grey13", size = 0.5, alpha = 0.3) +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.title = element_text(size = 10),
        plot.caption = element_text(size = 8),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank()) +
  labs(title = "Lack of Health Insurance",
       caption = 
         "Points represent 500 most populated cities in the US,\n excluding Hawaii and Alaska") +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, expend_map}
usa = map_data("state") %>%
  rename(state = "region")
cdc_df_map = read_csv("./data/cdc_df.csv") %>%
  separate(Geolocation, into = c("long", "lat"), sep = ",") %>%
  mutate(long = str_replace(long, "\\(", ""),
         lat = str_replace(lat, "\\)", ""),
         long = as.numeric(long),
         lat = as.numeric(lat),
         state = factor(state),
         state = tolower(state)) %>%
  filter(!state %in% c("alaska", "hawaii")) %>%
  left_join(., usa, by = "state")
ggplot() + 
  geom_polygon(data = cdc_df_map, aes(x = long.y, y = lat.y, 
                                      group = state, fill = health_exp), color = "white") +
  scale_fill_gradient2(low = "red", mid = "white", high = "blue", space = "Lab",
                       midpoint = mean(cdc_df_map$health_exp),
                       name = "US Dollars") +
  coord_fixed(1) +
  geom_point(data = cdc_df_map, aes(x = lat.x, y = long.x), 
             color = "grey13", size = 0.5, alpha = 0.3) +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.title = element_text(size = 10),
        plot.caption = element_text(size = 8),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank()) +
  labs(title = "Healthcare Expenditure per Capita",
       caption = 
         "Points represent 500 most populated cities in the US,\n excluding Hawaii and Alaska") + 
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, region_boxplot}
cdc_df %>%
  distinct(state, .keep_all = TRUE) %>%
  mutate(text_label = str_c("Health Expenditures per Capita: ", health_exp, '\nState: ', StateAbbr)) %>%
  mutate(region = fct_reorder(region, health_exp)) %>%
  plot_ly(y = ~health_exp, color = ~region, type = "box", text = ~text_label) %>%
  layout(
    xaxis = list(title = "Region"),
    yaxis = list(title = "Health Expenditures per Capita per State"),
    title = "Comparing Healthcare Expenditure Across Regions",
    font = "Open Sans",
    titlefont = "Open Sans"
  )
```

```{r, echo = FALSE}
reg = cdc_df %>%
  distinct(state, .keep_all = TRUE) %>%
  mutate(region = fct_reorder(region, health_exp)) %>%
  lm(health_exp ~ region, data = .)
anova(reg) %>% 
  broom::tidy() %>% 
  knitr::kable()
term = c("Region")
test = c("ANOVA")
test_stat = c(7.43803)
p_value = c(0.0003559)
regional_anova = tibble(
  "Term" = term,
  "Test" = test,
  "Test Statistic" = test_stat,
  "P-Value" = p_value
)
regional_anova %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")
```

## Discussion:  

Starting with health insurance, we found that there is a negative correlation between lack of health insurance and prevalence of proactive health practices, which include screening for diseases, and a positive correlation between variables pertaining to poor physical health. The notable exception was the routine checkups variable. There was no association between percent uninsured and the prevalence of routine checkups. This could indicate that there is a cost factor to these associations.
Having established an association between insurance and preventative care, we next analyzed the predictive ability of health practices on health outcomes. We found that the health practice variables from the dataset have the most predictive power for prevalence of cancer, and the least for high cholesterol. Intuitively, this makes sense for a couple of reasons. First, cholesterol levels are highly related to genetics, and this dataset has no variables collected on genetics. Also, many of the practices measured by this dataset are cancer screening practices. Cancer screening and other proactive health practices that we have mentioned tend to be very expensive, particularly for the uninsured. Since we know cost is often prohibitive, we next wanted to see if healthcare expenditure is uniform across the United States. Regional health expenditure analysis showed that there is a significant difference in healthcare expenditure between regions.   
Lastly, we inspected the relationships between specific diseases and health expenditure and percent uninsured. For most diseases, percent uninsured was found to have a positive association with disease. However, this trend is reversed with cancer. But, the relationship between health expenditures and prevalence of disease did not vary with disease.  
Overall, we found that the relationships between health insurance coverage, disease, and health practices is incredibly intricate and we've only scratched the surface of these questions of interest.