---
title: "p8105_fp_mjcr"
output: github_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(httr)
library(rvest)
library(openintro)
library(ggmap)

library(patchwork)


```

Download data:

```{r, cache = TRUE, message = FALSE}
#cdc_df = GET("https://chronicdata.cdc.gov/resource/ta23-kdpu.csv") %>%
#  content("parsed") 

cdc_df = read_csv("./data/500_Cities__City-level_Data__GIS_Friendly_Format___2016_release.csv")

```

Select variables we may be interested in:

```{r}

cdc_df = cdc_df %>%
  select(c(StateAbbr, PlaceName, Population2010, ACCESS2_AdjPrev, BPHIGH_AdjPrev, BPMED_AdjPrev, CANCER_AdjPrev, CHD_AdjPrev, CHECKUP_AdjPrev, CHOLSCREEN_AdjPrev, COLON_SCREEN_AdjPrev, COPD_AdjPrev,COREM_AdjPrev, COREW_AdjPrev, DENTAL_AdjPrev, DIABETES_AdjPrev, HIGHCHOL_AdjPrev, LPA_AdjPrev, MAMMOUSE_AdjPrev, OBESITY_AdjPrev, PAPTEST_AdjPrev, PHLTH_AdjPrev, STROKE_AdjPrev, Geolocation)) %>% 
  mutate(state = abbr2state(StateAbbr)) %>%
  select(state, everything())

```

Merge data on state expenditure on healthcare:

```{r, message = FALSE}
#link: https://www.kff.org/other/state-indicator/health-spending-per-capita/?currentTimeframe=0&sortModel=%7B%22colId%22:%22Location%22,%22sort%22:%22asc%22%7D

#Importing the raw expenditure data set and cleaning
healthcare_exp_df = read_csv("./data/health_care_expenditure.csv", 
                             skip = 4, n_max = 51, col_names = F) %>%
  rename(state = "X1", health_exp = "X2") %>%
  mutate(health_exp = str_replace(health_exp, "\\$", ""),
         health_exp  = as.numeric(health_exp))


#Add state healthcare expenditure data to CDC data
cdc_df = left_join(cdc_df, healthcare_exp_df, by = "state")

cdc_df = cdc_df %>% mutate(state = abbr2state(StateAbbr))

```

Merge data regions per state:

```{r, message = FALSE}
regions_df = read_csv("https://raw.githubusercontent.com/cphalpert/census-regions/master/us%20census%20bureau%20regions%20and%20divisions.csv") %>%
  janitor::clean_names() %>%
  select(-state_code)
  

cdc_df = left_join(cdc_df, regions_df, by = "state")
```

Create data dictionary:

```{r}
full_data_dictionary = readxl::read_xlsx("./data/data_dictionary.xlsx") 
full_data_dictionary = full_data_dictionary %>%
  janitor::clean_names() %>%
  filter(column_name %in% c("StateAbbr", "PlaceName", "Population2010", "ACCESS2_AdjPrev", "BPHIGH_AdjPrev", "BPMED_AdjPrev", "CANCER_AdjPrev", "CHD_AdjPrev", "CHECKUP_AdjPrev", "CHOLSCREEN_AdjPrev", "COLON_SCREEN_AdjPrev", "COPD_AdjPrev", "COREM_AdjPrev", "COREW_AdjPrev", "DENTAL_AdjPrev", "DIABETES_AdjPrev", "HIGHCHOL_AdjPrev", "LPA_AdjPrev", "MAMMOUSE_AdjPrev", "OBESITY_AdjPrev", "PAPTEST_AdjPrev", "PHLTH_AdjPrev", "STROKE_AdjPrev", "Geolocation"))

health_exp_dictionary = tibble(column_name = c("state", "health_exp"),
                               description = c("full name of the state", "total healthcare expenditures per capita by state in 2014"),
                               type = c("Plain Text", "Number"))

full_data_dictionary = full_join(full_data_dictionary, health_exp_dictionary)

region_dict = tibble(column_name = c("region", "division"),
                     description = c("geographical region of the state", "more specific division within the region"),
                     type = c("Plain Text", "Plain Text")
  
)

full_data_dictionary = full_join(full_data_dictionary, region_dict)
```

Export merged data:

```{r}
write_csv(cdc_df, path = "./data/cdc_df.csv")
write_csv(full_data_dictionary, path = "./data/full_data_dictionary.csv")
```


List of health practice variables and health outcome variables:

```{r}
health_practices = cdc_df %>%
  select(BPMED_AdjPrev, CHECKUP_AdjPrev, CHOLSCREEN_AdjPrev, COLON_SCREEN_AdjPrev, COREM_AdjPrev, COREW_AdjPrev, DENTAL_AdjPrev, LPA_AdjPrev, MAMMOUSE_AdjPrev, PAPTEST_AdjPrev)

health_outcomes = cdc_df %>%
  select(BPHIGH_AdjPrev, CANCER_AdjPrev, CHD_AdjPrev, COPD_AdjPrev, DIABETES_AdjPrev, HIGHCHOL_AdjPrev, OBESITY_AdjPrev, PHLTH_AdjPrev, STROKE_AdjPrev)

miscellaneous = cdc_df %>%
  select(StateAbbr, PlaceName, Population2010, ACCESS2_AdjPrev, Geolocation, state, health_exp, region, division)
```




Analyze some variables: region

```{r}

cdc_df %>%
  distinct(state, .keep_all = TRUE) %>%
  mutate(region = fct_reorder(region, health_exp)) %>%
  lm(health_exp ~ region, data = .) %>%
  summary

cdc_df %>%
  distinct(state, .keep_all = TRUE) %>%
  mutate(division = fct_reorder(division, health_exp)) %>%
  lm(health_exp ~ division, data = .) %>%
  summary

cdc_df %>%
  lm(health_exp ~ ACCESS2_AdjPrev, data = .) %>%
  summary


```


Analyze some variables: expenditure

```{r}
cdc_df %>%
  lm(DIABETES_AdjPrev ~ CHECKUP_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(OBESITY_AdjPrev ~ health_exp + CHECKUP_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(BPHIGH_AdjPrev ~ health_exp + CHECKUP_AdjPrev, data = .) %>%
  summary

library(betareg)

cdc_df %>%
  mutate(DIABETES_AdjPrev = DIABETES_AdjPrev/100,
         CHECKUP_AdjPrev = CHECKUP_AdjPrev/100) %>%
  betareg(DIABETES_AdjPrev ~ CHECKUP_AdjPrev + health_exp, data = .) %>%
  summary


```


Analyzing relationship b/w insurance and health practices:

```{r}
cdc_df %>%
  lm(ACCESS2_AdjPrev ~ CHECKUP_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ DENTAL_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ CHOLSCREEN_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ COLON_SCREEN_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ COREM_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ COREW_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ LPA_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ MAMMOUSE_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ PAPTEST_AdjPrev, data = .) %>%
  summary

cdc_df %>%
  lm(ACCESS2_AdjPrev ~ PHLTH_AdjPrev, data = .) %>%
  summary
```


```{r}
dental = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = DENTAL_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("Dental")

chol = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = CHOLSCREEN_AdjPrev, color = region)) + 
  geom_point()

colon = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = COLON_SCREEN_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("Colon Screening")

corem = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = COREM_AdjPrev, color = region)) + 
  geom_point()

corew = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = COREW_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("Women w/ all Preventative Services")

lpa = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = LPA_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("No Physical Activity")

mammouse = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = MAMMOUSE_AdjPrev, color = region)) + 
  geom_point()

obesity = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = OBESITY_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("Obesity")

paptest = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = PAPTEST_AdjPrev, color = region)) + 
  geom_point()

phlth = cdc_df %>% 
  ggplot(aes(x = ACCESS2_AdjPrev, y = PHLTH_AdjPrev)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  xlab("% Without Insurance") +
  ylab("Poor Physical Health")

(dental | colon | corew) / (obesity | lpa | phlth)
```

Regional insurance boxplot

```{r, echo = FALSE, message = FALSE, cache = TRUE}
read_csv("./data/cdc_df.csv") %>%
  mutate(region = fct_reorder(region, ACCESS2_AdjPrev),
         text_label = str_c("% Lack Health Insurance: ", 
                            ACCESS2_AdjPrev, '\nCity: ', PlaceName)) %>%
  plot_ly(y = ~ACCESS2_AdjPrev, color = ~region, type = "box", text = ~text_label) %>%
  layout(yaxis = list(title = "Percent Lack Health Insurance"),
    title = "Comparing Lack of Health Insurance Across Regions"
  )
```


